Tool for Visual Cluster Analysis and Consensus Clustering

### 2020-05-08 presentation/presentation.tex
presentation
pagenumber
fixed image
quote

\documentclass[aspectratio=169]{beamer}

\usepackage[backend=bibtex]{biblatex}
\bibliography{../thesis/references}
%\bibliographystyle{ieeetr}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

@@

\title[Consensus Clustering]{Tool for Visual Cluster Analysis and Consensus Clustering}
\author{Christian Permann}
\institute{Faculty of Computer Science, University of Vienna,\newline W\"ahringer Stra{\ss}e 29, 1090 Vienna}
\date{TBD.04.2020}

@@

\begin{frame}{Introduction}
	Clustering:
	\begin{itemize}
		\item Grouping data-points such that their underlying relationships are reflected
		\item Gaining knowledge through this grouping
	\end{itemize}

	\begin{center}
		The process of clustering is not done when a solution is computed,\newline but when the researcher involved:\newline
		``... \textbf{evaluated}, \textbf{understood} and \textbf{accepted} the patterns.'' (Chen and Liu \cite{VISTA})
	\end{center}

@@

\begin{frame}{Related Work: Clustering}
	There is a vast amount of clustering techniques, including:\newline
	\begin{itemize}
		\item Partition-based methods (KMeans-like algorithms)
		\item Hierarchy-based methods (e.g. Joining of Sets/Linking)
		\item Density-based methods (e.g. DBSCAN/OPTICS)
		\begin{itemize}
			\item Many more...
		\end{itemize}
	\end{itemize}
\end{frame}

@@

	\begin{figure}
	  \centering
	    \includegraphics[width=.64\textwidth]{unob}
	  \caption{Data-View}
	  \label{fig:data-view}
	\end{figure}

@@

@@

\begin{frame}{Tests: Unobtainable Solutions}
	\begin{figure}[h]
		\centering
		\includegraphics[width=.64\textwidth]{unob}
		\caption{Synthetic Data with Ground Truth}
		\label{fig:better_base}
	\end{figure}
\end{frame}

@@

@@

\begin{frame}[allowframebreaks]{References}
\printbibliography
\end{frame}

>>>>

\documentclass[aspectratio=169]{beamer}
\usepackage[backend=bibtex]{biblatex}

\bibliography{../thesis/references}
%\bibliographystyle{ieeetr}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  \setbeamertemplate{footline}[frame number]
}

@@

\title[Consensus Clustering]{Tool for Visual Cluster Analysis and Consensus Clustering}
\author{Christian Permann}
\institute{Faculty of Computer Science, University of Vienna,\newline W\"ahringer Stra{\ss}e 29, 1090 Vienna}
\date{12.05.2020}

\newcommand{\backupbegin}{
   \newcounter{finalframe}
   \setcounter{finalframe}{\value{framenumber}}
}
\newcommand{\backupend}{
   \setcounter{framenumber}{\value{finalframe}}
}

@@

\begin{frame}{Introduction}
	Clustering:
	\begin{itemize}
		\item Grouping data-points such that their underlying relationships are reflected
		\item Gaining knowledge through this grouping
		\item[]
	\end{itemize}

	The process of clustering is only done when the user:
	\begin{center}
		``... \textbf{evaluated}, \textbf{understood} and \textbf{accepted} the patterns.'' (Chen and Liu \cite{VISTA})
	\end{center}

@@

\begin{frame}{Related Work: Clustering}
	There is a vast amount of clustering techniques, including:\newline
	\begin{itemize}
		\item Partition-based methods (KMeans-like algorithms)
		\item Hierarchy-based methods (e.g. Joining of Sets/Linking)
		\item Density-based methods (e.g. DBSCAN/OPTICS)
		\item[]
		\begin{itemize}
			\item Many more...
		\end{itemize}
	\end{itemize}
\end{frame}

@@

	\begin{figure}
	  \centering
	    \includegraphics[width=.64\textwidth]{unob_fix}
	  \caption{Data-View}
	  \label{fig:data-view}
	\end{figure}

@@

\begin{frame}{Recoloring Clusterings for Comparison}

	\begin{figure}
	  \centering
	    \includegraphics[width=.51\textwidth]{my-hungarian}
	  \caption{Depiction of Hungarian's Method }
	  \label{fig:hungarian}
	\end{figure}

@@

\begin{frame}{Tests: Unobtainable Solutions}
	\begin{figure}[h]
		\centering
		\includegraphics[width=.64\textwidth]{unob_fix}
		\caption{Synthetic Data with Ground Truth}
		\label{fig:better_base}
	\end{figure}
\end{frame}

@@

\begin{frame}{Tests: Finding a good Sampling Range}

	\begin{itemize}
	 	\item User testing on QCM3 data-set (different alcohols passed through sensors)
		\item Sampling with K-Means Algorithm, 10 samples per $k$
	\end{itemize}
	\begin{figure}[h]
		\centering
		\begin{subfigure}[t]{.49\textwidth}
			  \centering
			  \includegraphics[width=.99\linewidth]{user_qcm_optics}
			  \caption{K-Means results with: $k= 2..20$ \\ ($k>10$ grayed out)}
			  \label{fig:user_wifi_consensus}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{.49\textwidth}
			  \centering
			  \includegraphics[width=.99\linewidth]{user_qcm_optics2}
			  \caption{K-Means results with: $k= 2..10$}
			  \label{fig:user_wifi_best}
		\end{subfigure}

		\caption{OPTICS Plots for different Sampling Ranges}
		\label{fig:user_wifi}
	\end{figure}
\end{frame}

@@

\appendix
\backupbegin

\begin{frame}[allowframebreaks]{References}
\printbibliography
\end{frame}
\backupend
